Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-03-15 analysis/memo_TAS_reviewers.Rmd
type correction b_curr to b_{curr}

It is true, based on our simulations, that bias can be erroneously detected (i.e. even if $b_curr$ = 0), if there are many past trials (e.g., n = 3) and in the bias in those trials exhibits strong incompatibility. On the other hand, given high compatibility, low values of $\alpha$ increase Type I error.  This is why we recommend using different values of $\alpha$ to check for sensitivity. See Item 1(2) above.

@@

Similarly, although we did run simulations for when when $\alpha = 0$, Figures 2-4 do not depict the bias detection rate for that scenario, simply because that scenario is equivalent to evaluating bias detection with only strike data from the current trial (no historical strike data) -- a topic of prior papers [e.g. @Kadane2018a].

>>>>

It is true, based on our simulations, that bias can be erroneously detected (i.e. even if $b_{curr}$ = 0), if there are many past trials (e.g., n = 3) and in the bias in those trials exhibits strong incompatibility. On the other hand, given high compatibility, low values of $\alpha$ increase Type I error.  This is why we recommend using different values of $\alpha$ to check for sensitivity. See Item 1(2) above.

@@

Similarly, although we did run simulations for when $\alpha = 0$, Figures 2-4 do not depict the bias detection rate for that scenario, simply because that scenario is equivalent to evaluating bias detection with only strike data from the current trial (no historical strike data) -- a topic of prior papers [e.g. @Kadane2018a].
